---
title: "Telecom Customer Retention"
output: html_notebook
---


## 1. Installing packages 



```{r}
install.packages("tidyverse")
```

#### Load tidyverse for use in our notebook
```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
```

## 2. Data Importation



```{r}


telecomcust_df <- read_csv("telecom_customer.csv")
telecomcust_df
```



```{r}

sample_n(telecomcust_df, 10)
```

```{r}


dim(telecomcust_df)
```





##  Performing Standardisation



```{r}
telecom_df <- read_csv("telecom_customer.csv")
telecom_df

# Strip the leading and trailing spaces
names(telecom_df) <- trimws(names(telecom_df), which = c("both"))
names(telecom_df)

```


```{r}
names(telecom_df) <- tolower(names(telecom_df))
names(telecom_df)
```



## 5. Handling Irrelevant Data

### Dropping customer_id column

```{r}
head(telecom_df)

telecom_df = select(telecom_df, -c("customerid"))
head(telecom_df)
```



```{r}
# Let's determine the number of records using dim()
dim(telecom_df)
```



```{r}

unique(telecom_df)

```

```{r}

summary(telecom_df)

```

### Metric of Success 
### solution will have satisfied the research question when you can identify the factors that contribute to customer churn.

```{r}

head(telecom_df)
```




### What number of customers who left within the last month ?

```{r}
ggplot(data = telecom_df , aes(x = churn,fill = churn)) + geom_bar()  + geom_text(stat = 'count' , aes(label = paste("n = " , formatC(..count..))),vjust = -0.5) + theme_minimal() + ggtitle("Number of customer churn") + theme(plot.title = element_text(hjust = 0.5))
```
### What type of internet services do customers have ?
```{r}
ggplot(data = telecom_df, aes(x = churn,fill = internetservice)) + geom_bar(stat = "count",position = position_dodge()) + geom_text(stat = "count" , aes(label = paste("n = " , formatC(..count..))),vjust = -0.5 , position = position_dodge(0.9)) + ggtitle("Customer Churn by Internet Services") + theme_minimal() + theme(plot.title = element_text(hjust = 0.5))

```
## highest chyrn rate is on fiber optic as an internet service 

## What a number of churn cutomers by gender ?



```{r}

ggplot(data = telecom_df, aes(x = churn,fill = gender)) + geom_bar(stat = "count",position = position_dodge()) + geom_text(stat = "count" , aes(label = paste("n = " , formatC(..count..))),vjust = -0.5 , position = position_dodge(0.9)) + ggtitle("Customers Churn by Gender") + theme_minimal() + theme(plot.title = element_text(hjust = 0.5))
```

## Churn rate is the same  for both vendors